Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-07-13 paper/main.Rmd
deleted the contributions to paper paragraph

Our contributions in this paper are:

@@

 * introduce a distance measure for detecting distributional difference in temporal granularities, which enables identification
of patterns in the time series data;

 * devise a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns;

 * show that the proposed distance metric could be used to rank the interesting patterns across different datasets and temporal granularities since they have been normalized for relevant parameters.

\noindent The article is organized as follows. Section \ref{sec:computation-wpd} introduces a new distance measure, discusses the reasoning and details the computation.  Section \ref{sec:rank-wpd} discusses how to choose a threshold to select only useful displays. Section \ref{sec:simulations} provides some simulation study on the proposed methodology. Section \ref{sec:application-wpd} presents an application to residential smart meter data in Melbourne to show how the proposed methodology can be used to automatically detect temporal granularities along which distributional differences are significant.

>>>>

<!-- Our contributions in this paper are: -->

@@

 <!-- *  -->

 <!-- * ; -->

 <!-- * show that the proposed distance metric could be used to rank the interesting patterns across different datasets and temporal granularities since they have been normalized for relevant parameters. -->

\noindent The article is organized as follows. Section \ref{sec:computation-wpd} introduces a distance measure for detecting distributional difference in temporal granularities, which enables identification of patterns in the time series data;
Section \ref{sec:rank-wpd} devises a selection criterion by choosing a threshold, which results in detection of only significantly interesting patterns. Section \ref{sec:simulations} provides some simulation study on the proposed methodology. Section \ref{sec:application-wpd} presents an application to residential smart meter data in Melbourne to show how the proposed methodology can be used to automatically detect temporal granularities along which distributional differences are significant.
